Estimating Predictive Rate-Distortion via Neural Variational Inference

### 2019-03-06 paper.tex
Updates from Overleaf

@@

People have studied information density as a model of cost in human language processing.

But also memory cost is relevant

>>>>

Natural language has been a testing ground for information-theoretic ideas since Shannon's work.
Much interest has been devoted to the study of the entropy rate of language.
....

Indeed, the information density of language has been linked to human processing effort.

The Uniform Information Density and Constant Entropy Rate hypotheses

The word-by-word surprisal has been shown to be an accurate linear predictor of human processing effort as measured by per-word reading times.

Human do prediction

There is the related question of how much memory is needed to predict.

This is captured by NPRD: human memory vs surprisal

In psycholinguistics, memory known to impact processing.

Futrell and Levy

@@

%People have studied information density as a model of cost in human language processing.

%But also memory cost is relevant
